---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# leb-tpd-pipeline-2020

<!-- badges: start -->
<!-- badges: end -->

This is the repository containing an internal presentation about the Lebanon TPD Data Pipeline project, an example of future continuous integration work to streamline data flow for transparency and reproducibility.

## Installation

If you'd like to play around with the materials here, do these tasks: 

1. `git clone` this repo into your folder of choice (you can also use the `Code > Download ZIP...` button). 
1. Open the `.Rproj` file in RStudio
1. Run this command in the console:

```{r, eval=FALSE}
source("install.R")
```

That should install all of the packages needed to build this presentation and run the example drake workflow.

Note: it may yell at you about a "GitHub personal access token". See [this blurb in _Happy Git with R_](https://happygitwithr.com/github-pat.html#step-by-step) for more information and context.
